Whole-body connectome of a segmented annelid larva

### 2024-03-19 Manuscript.qmd
MS: changed author field, added toc

---
title: "Whole-body connectome of a segmented annelid larva"
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: default
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: false
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---
\

Gáspár Jékely^1,2,\*^ , Sanja Jasek^1,2^, Martin Gühmann^3^, Luis Alberto Bezares Calderón^2^, Elizabeth A. Williams^4^, Réza Shahidi^5^\

^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany\
^2^Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom\
^3^School of Biological Sciences, University of Bristol, Bristol, United Kingdom\
^4^BioSciences, University of Exeter, Stocker Road, Exeter EX4 4QD, Exeter, United Kingdom\
^5^Electron Microscopy Core Facility (EMCF), University of Heidelberg, 69120 Heidelberg, Germany\
^\*^Correspondence: gaspar.jekely\@cos.uni-heidelberg.de

>>>>

---
title: "Whole-body connectome of a segmented annelid larva"
subtitle: |
  \raggedright  Gáspár Jékely^1,2,\*^ , Sanja Jasek^1,2^, Martin Gühmann^3^, Luis Alberto Bezares-Calderón^2^, Elizabeth A. Williams^4^, Réza Shahidi^5^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Living Systems Institute, University of Exeter, Exeter, EX4 4QD, United Kingdom \newline<br>^3^School of Biological Sciences, University of Bristol, Bristol, United Kingdom \newline<br>^4^BioSciences, University of Exeter, Stocker Road, Exeter EX4 4QD, Exeter, United Kingdom\newline<br> ^5^Electron Microscopy Core Facility (EMCF), University of Heidelberg, 69120 Heidelberg, Germany \newline<br> ^\*^Correspondence: gaspar.jekely@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: default
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---
